---
title: "Shiny_Wrangle"
author: "Flynn McMorrow"
date: "7/20/2021"
output: html_document
---

#Library and Working Directory
```{r}
library(shiny)
library(DT)
library(shinydashboard)
library(magrittr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(naniar)
library(gtsummary)
library(gt)
library(webshot2)
library(cowplot)
library(colourpicker)
library(stringr)
library(ggmosaic)
library(shinyvalidate)
library(ggpubr)
library(ggrepel)
library(forcats)
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
```

#Primary Groups
```{r}
display_type <- c("Count", "Percent")

safe_colorblind_palette <- c("#88CCEE", "#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888")

missing_data <- c("Yes", "No")

caption <- c("No", "Yes")

dataset_choice <- c("MAPP I Baseline", "MAPP II Baseline", "MAPP I Longitudinal", "MAPP II Longitudinal")
dataset_choice_long <- c("MAPP I Longitudinal", "MAPP II Longitudinal")
dataset_choice_dict <- c("MAPP I Baseline", "MAPP II Baseline", "MAPP I Longitudinal", "MAPP II Longitudinal")

pdf_png <- c(".pdf", ".png")
```

#MAPP BL 1
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_bl_2 <- read.csv("mapp_bl_2.csv") %>%
  mutate(cohorttype2 = ifelse(cohorttype == 1, "1 - UCPPS", ifelse(cohorttype == 2, "2 - Healthy Controls", "3 - Positive Controls"))) %>% 
  select(-pid)
mapp_bl_2[mapp_bl_2 == "."] <- NA
mapp_bl_2[mapp_bl_2 == " "] <- NA
mapp_bl_2[sapply(mapp_bl_2, is.character)] <- lapply(mapp_bl_2[sapply(mapp_bl_2, is.character)], as.factor)

mapp_bl_cohort <- mapp_bl_2 %>% 
  select(cohorttype2) %>% 
  distinct(cohorttype2, .keep_all = TRUE)
```

#Variable Assignment 3
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_dict <- read.csv("variable_dict.csv")

variable_assignments_3 <- mapp_dict %>% 
  mutate(variable = as.character(NAME), variable_selection = as.character(Primary_Grouping), label = as.character(Label)) %>% 
  mutate(ANALYSIS_TYPE_2 = ifelse(ANALYSIS_TYPE == 1, "1 - Continuous", ifelse(ANALYSIS_TYPE == 2, "2 - Ordinal", ifelse(ANALYSIS_TYPE == 3, "3 - Nominal", "4 - Binary")))) %>% 
  select(variable, variable_selection, ANALYSIS_TYPE, ANALYSIS_TYPE_2, label) %>% 
  filter(variable != "pid" & variable != "zip_first3" & variable != "year_visit")

mapp_bl_primary <- variable_assignments_3 %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#MAPP BL Labels
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")

mapp_bl_labels <- read.csv("mapp_bl_label.csv") %>% 
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")),  
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat), 
         copc_sum3_ord3 = ifelse(copc_sum3_ord3 == "0:00", "0: 0", copc_sum3_ord3),
         copc_sum5_ord3 = ifelse(copc_sum5_ord3 == "0:00", "0: 0", copc_sum5_ord3),
         across(starts_with("medtype"), ~ ifelse(. == "1:01", "1: 1", .))) %>% 
  select(-pid)

mapp_bl_labels[mapp_bl_labels == "."] <- NA
mapp_bl_labels[mapp_bl_labels == " "] <- NA
mapp_bl_labels[sapply(mapp_bl_labels, is.character)] <- lapply(mapp_bl_labels[sapply(mapp_bl_labels, is.character)], as.factor)

variable_assignments_4 <- variable_assignments_3 %>% 
  filter(ANALYSIS_TYPE != 1 & variable != "pid")

variable_assignments_5 <- variable_assignments_3 %>% 
  filter(ANALYSIS_TYPE == 1 & variable != "pid")

factored <- mapp_bl_labels %>% 
  select(any_of(variable_assignments_4$variable)) %>% 
  mutate_if(is.numeric, as.factor) %>% 
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")))

continuous <- mapp_bl_2 %>% 
  select(any_of(variable_assignments_5$variable))

mapp_bl_combined <- data.frame(factored, continuous) %>% 
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")))

mapp_bl_combined[sapply(mapp_bl_combined, is.character)] <- lapply(mapp_bl_combined[sapply(mapp_bl_combined, is.character)], as.factor)
```

#Full Labels
```{r}
full_labels <- mapp_dict %>%
  select(NAME, Label) %>% 
  rename(variable_label = Label, variable = NAME)
```

#**MAPP II Baseline**

#Dictionary
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_dict_II <- read.csv("variable_dict_II.csv") %>% 
  select(1:11)
```

#Variable Assignments 3, 4, 5
```{r}
variable_assignments_3_II <- mapp_dict_II %>% 
  mutate(variable = as.character(NAME), variable_selection = as.character(Primary_Grouping), label = as.character(LABEL)) %>% 
  mutate(ANALYSIS_TYPE_2 = ifelse(ANALYSIS_TYPE == 1, "1 - Continuous", ifelse(ANALYSIS_TYPE == 2, "2 - Ordinal", ifelse(ANALYSIS_TYPE == 3, "3 - Nominal", "4 - Binary")))) %>% 
  select(variable, variable_selection, ANALYSIS_TYPE, ANALYSIS_TYPE_2, label) %>% 
  filter(variable != "pid" & variable != "zip_first3" & variable != "year_visit")
```

#MAPP BL 2 II
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_bl_2_II <- read.csv("mapp_bl_2_II.csv") %>%
  mutate(cohorttype2 = ifelse(cohorttype == 1, "1 - UCPPS", ifelse(cohorttype == 2, "2 - Healthy Controls", "3 - Positive Controls"))) %>% 
  select(-pid)
mapp_bl_2_II[mapp_bl_2_II == "."] <- NA
mapp_bl_2_II[mapp_bl_2_II == " "] <- NA
mapp_bl_2_II[sapply(mapp_bl_2_II, is.character)] <- lapply(mapp_bl_2_II[sapply(mapp_bl_2_II, is.character)], as.factor)

mapp_bl_cohort_II <- mapp_bl_2_II %>% 
  select(cohorttype2) %>% 
  distinct(cohorttype2, .keep_all = TRUE)

mapp_bl_primary_II <- variable_assignments_3_II %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#MAPP Labels II
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_bl_labels_II <- read.csv("mapp_bl_label_II.csv") %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")),
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat), 
         copc_sum3_ord3 = ifelse(copc_sum3_ord3 == "0:00", "0: 0", copc_sum3_ord3),
         copc_sum5_ord3 = ifelse(copc_sum5_ord3 == "0:00", "0: 0", copc_sum5_ord3)) %>%
  select(-pid)

mapp_bl_labels_II[mapp_bl_labels_II == " "] <- NA
mapp_bl_labels_II[mapp_bl_labels_II == "."] <- NA
mapp_bl_labels_II[sapply(mapp_bl_labels_II, is.character)] <- lapply(mapp_bl_labels_II[sapply(mapp_bl_labels_II, is.character)], as.factor)

variable_assignments_4_II <- variable_assignments_3_II %>% 
  filter(ANALYSIS_TYPE != 1 & variable != "pid")

variable_assignments_5_II <- variable_assignments_3_II %>% 
  filter(ANALYSIS_TYPE == 1 & variable != "pid")

factored_II <- mapp_bl_labels_II %>%
  select(any_of(variable_assignments_4_II$variable)) %>%
  mutate_if(is.numeric, as.factor)

continuous_II <- mapp_bl_2_II %>%
  select(any_of(variable_assignments_5_II$variable))

mapp_bl_combined_II <- data.frame(factored_II, continuous_II) %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Controls", "2 - Healthy Controls", "3 - Positive Controls")),
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat))

mapp_bl_combined_II[sapply(mapp_bl_combined_II, is.character)] <- lapply(mapp_bl_combined_II[sapply(mapp_bl_combined_II, is.character)], as.factor)

setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
full_labels_II <- read_csv("full_labels_II.csv") %>% 
  select(1:2)
```

#**Longitudinal Data**

#Loading in Longitudinal Data
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_long_labels <- read_csv("formatted_m1longdata_26aug2022.csv", na = ".")
mapp_long_raw <- read_csv("unformatted_m1longdata_26aug2022.csv", na = "")
mapp_long_dict <- read_csv("M1 longitudinal data assignments 26aug2022.csv") %>% 
  rename(variable = NAME, label = LABEL, analysis_type = ANALYSIS_TYPE, variable_selection = Primary_Grouping)
```

#Cleaning Longitudinal Raw Data
```{r}
mapp_long_raw <- mapp_long_raw %>%
  mutate(cohorttype2 = ifelse(cohorttype == 1, "1 - UCPPS", NA))

mapp_long_cohort <- mapp_long_raw %>% 
  select(cohorttype2) %>% 
  distinct(cohorttype2, .keep_all = TRUE)
```

#Variable Assingment Longitudinal
```{r}
variable_assignments_long_3 <- mapp_long_dict %>% 
  mutate(ANALYSIS_TYPE_2= ifelse(analysis_type == 1, "1 - Continuous", ifelse(analysis_type == 2, "2 - Ordinal", ifelse(analysis_type == 3, "3 - Nominal", "4 - Binary")))) %>% 
  select(variable, variable_selection, analysis_type, ANALYSIS_TYPE_2, label)

mapp_long_primary <- variable_assignments_long_3 %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#MAPP Long Labels
```{r}
mapp_long_labels <- mapp_long_labels %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", NA),
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat),
         copc_sum3_ord3 = ifelse(copc_sum3_ord3 == "0:00", "0: 0", copc_sum3_ord3),
         copc_sum5_ord3 = ifelse(copc_sum5_ord3 == "0:00", "0: 0", copc_sum5_ord3),
         across(starts_with("medtype"), ~ ifelse(. == "1:01", "1: 1", .)),
         pid = as.factor(pid))

mapp_long_labels[sapply(mapp_long_labels, is.character)] <- lapply(mapp_long_labels[sapply(mapp_long_labels, is.character)], as.factor)

variable_assignments_long_4 <- variable_assignments_long_3 %>%
  filter(analysis_type != 1)

variable_assignments_long_5 <- variable_assignments_long_3 %>%
  filter(analysis_type == 1)

factored_long <- mapp_long_labels %>%
  select(any_of(variable_assignments_long_4$variable)) %>%
  mutate_if(is.numeric, as.factor)

continuous_long <- mapp_long_raw %>%
  select(any_of(variable_assignments_long_5$variable))

mapp_long_combined <- data.frame(factored_long, continuous_long) %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")))

mapp_bl_combined[sapply(mapp_bl_combined, is.character)] <- lapply(mapp_bl_combined[sapply(mapp_bl_combined, is.character)], as.factor)

mapp_long_primary_con <- variable_assignments_long_5 %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#Full Labels Long
```{r}
full_labels_long <- as.data.frame(mapp_long_dict %>%
  select(variable, label) %>% 
  rename(variable_label = label))
```

#Longitudinal Groups
```{r}
mapp_long_primary <- variable_assignments_long_3 %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#**Longitudinal Data II**

#Loading in Longitudinal Data II
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_long_labels_II <- read_csv("formatted_m1longdata_26aug2022.csv", na = ".")
mapp_long_raw_II <- read_csv("unformatted_m1longdata_26aug2022.csv", na = "")
mapp_long_dict_II <- read_csv("M1 longitudinal data assignments 26aug2022.csv") %>% 
  rename(variable = NAME, label = LABEL, analysis_type = ANALYSIS_TYPE, variable_selection = Primary_Grouping)
```

#Cleaning Longitudinal Raw Data II
```{r}
mapp_long_raw_II <- mapp_long_raw_II %>%
  mutate(cohorttype2 = ifelse(cohorttype == 1, "1 - UCPPS", NA))

mapp_long_cohort_II <- mapp_long_raw_II %>% 
  select(cohorttype2) %>% 
  distinct(cohorttype2, .keep_all = TRUE)
```

#Variable Assingment Longitudinal II
```{r}
variable_assignments_long_3_II <- mapp_long_dict_II %>% 
  mutate(ANALYSIS_TYPE_2 = ifelse(analysis_type == 1, "1 - Continuous", ifelse(analysis_type == 2, "2 - Ordinal", ifelse(analysis_type == 3, "3 - Nominal", "4 - Binary")))) %>% 
  select(variable, variable_selection, analysis_type, ANALYSIS_TYPE_2, label)

mapp_long_primary_II <- variable_assignments_long_3_II %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#MAPP Long Labels II
```{r}
mapp_long_labels_II <- mapp_long_labels_II %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", NA),
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat),
         copc_sum3_ord3 = ifelse(copc_sum3_ord3 == "0:00", "0: 0", copc_sum3_ord3),
         copc_sum5_ord3 = ifelse(copc_sum5_ord3 == "0:00", "0: 0", copc_sum5_ord3),
         across(starts_with("medtype"), ~ ifelse(. == "1:01", "1: 1", .)),
         pid = as.factor(pid))

mapp_long_labels_II[sapply(mapp_long_labels_II, is.character)] <- lapply(mapp_long_labels_II[sapply(mapp_long_labels_II, is.character)], as.factor)

variable_assignments_long_4_II <- variable_assignments_long_3_II %>%
  filter(analysis_type != 1)

variable_assignments_long_5_II <- variable_assignments_long_3_II %>%
  filter(analysis_type == 1)

factored_long_II <- mapp_long_labels_II %>%
  select(any_of(variable_assignments_long_4_II$variable)) %>%
  mutate_if(is.numeric, as.factor)

continuous_long_II <- mapp_long_raw_II %>%
  select(any_of(variable_assignments_long_5_II$variable))

mapp_long_combined_II <- data.frame(factored_long_II, continuous_long_II) %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")))

mapp_bl_combined_II[sapply(mapp_bl_combined_II, is.character)] <- lapply(mapp_bl_combined_II[sapply(mapp_bl_combined_II, is.character)], as.factor)
```

#Full Labels Long II
```{r}
full_labels_long_II <- as.data.frame(mapp_long_dict_II) %>%
  select(variable, label) %>% 
  rename(variable_label = label)
```

#Longitudinal Groups II
```{r}
mapp_long_primary_II <- variable_assignments_long_3_II %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```