---
title: "Shiny_Wrangle"
author: "Flynn McMorrow"
date: "7/20/2021"
output: html_document
---

#Library and Working Directory
```{r}
library(shiny)
library(DT)
library(shinydashboard)
library(magrittr)
library(tidyverse)
library(dplyr)
library(naniar)
library(stringr)
library(gtsummary)
library(gt)
library(cowplot)
library(colourpicker)
library(stringr)
library(ggmosaic)
library(shinyvalidate)
library(ggpubr)
library(ggrepel)
library(forcats)
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
```

#Primary Groups
```{r}
display_type <- c("Count", "Percent")

safe_colorblind_palette <- c("#88CCEE", "#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888")

missing_data <- c("Yes", "No")

caption <- c("No", "Yes")

dataset_choice <- c("MAPP I Baseline", "Mapp II Baseline")
```

#MAPP BL 2
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_bl_2 <- read.csv("mapp_bl_2.csv") %>%
  mutate(cohorttype2 = ifelse(cohorttype == 1, "1 - UCPPS", ifelse(cohorttype == 2, "2 - Healthy Controls", "3 - Positive Controls")), sex = ifelse(sex == 1, "Male", "Female")) %>% 
  select(-pid)

mapp_bl_cohort <- mapp_bl_2 %>% 
  select(cohorttype2) %>% 
  distinct(cohorttype2, .keep_all = TRUE)

mapp_bl_sex <- mapp_bl_2 %>% 
  select(sex) %>% 
  distinct(sex, .keep_all = TRUE)

mapp_bl_primary <- variable_assignments_3 %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#Variable Assignment 3
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_dict <- read.csv("variable_dict.csv")

variable_assignments_3 <- mapp_dict %>% 
  slice(1:910) %>% 
  mutate(variable = as.character(NAME), variable_selection = as.character(Primary_Grouping), label = as.character(LABEL)) %>% 
  mutate(ANALYSIS_TYPE_2 = ifelse(ANALYSIS_TYPE == 1, "1 - Continuous", ifelse(ANALYSIS_TYPE == 2, "2 - Ordinal", ifelse(ANALYSIS_TYPE == 3, "3 - Nominal", "4 - Binary")))) %>% 
  select(variable, variable_selection, ANALYSIS_TYPE, ANALYSIS_TYPE_2, label) %>% 
  filter(variable != "pid" & variable != "zip_first3")
```

#MAPP Labels
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")

mapp_bl_labels <- read.csv("mapp_bl_label.csv") %>% 
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")),  
         sex = ifelse(sex == "1: Male", "Male", "Female"), bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat)) %>% 
  select(-pid)
mapp_bl_labels[mapp_bl_labels == "."] <- NA

variable_assignments_4 <- variable_assignments_3 %>% 
  filter(ANALYSIS_TYPE != 1 & variable != "pid")

variable_assignments_5 <- variable_assignments_3 %>% 
  filter(ANALYSIS_TYPE == 1 & variable != "pid")

factored <- mapp_bl_labels %>% 
  select(any_of(variable_assignments_4$variable)) %>% 
  mutate_if(is.numeric, as.factor)

continuous <- mapp_bl_2 %>% 
  select(any_of(variable_assignments_5$variable))

mapp_bl_combined <- data.frame(factored, continuous) %>% 
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")), 
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat))
```

#Labels and Levels
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
full_labels <- read_csv("full_labels.csv") %>% 
  drop_na()

factored %>% 
  summarise_all(n_distinct) %>% 
  gather(key = "variable", value = "n") %>% 
  filter(n > 6) %>% 
  arrange(desc(n))
```

#Testing drop_na
```{r}
mapp_bl_combined %>% 
  filter(cohorttype2 == "1 - UCPPS") %>% 
  select(age_dx_pbsic)
```

#bpi_numsites_pp
```{r}
unique(variable_assignments_3$ANALYSIS_TYPE_2)

variable_assignments_3 %>% 
  filter(variable == "bpi_numsites_pp")

variable_assignments_3 %>% 
  group_by(variable) %>%
  filter(n()>1) %>% 
  arrange(variable)

variable_assignments_3 %>% 
  group_by(variable) %>%
  filter(n()>1) %>% 
  arrange(variable) %>% 
  distinct(variable, .keep_all = TRUE)

variable_assignments_4 %>% 
  group_by(variable) %>%
  filter(n()>1) %>% 
  arrange(variable)
```


#Max/Min
```{r}
max(mapp_bl_2$pain_severity, na.rm = TRUE)
max(mapp_bl_2$urinary_severity, na.rm = TRUE)

qwerty <- mapp_bl_2 %>% 
  select(pain_severity)

max(qwerty, na.rm = TRUE)
min(qwerty, na.rm = TRUE)
```

#pain_severity Scaling Issue
```{r}
mapp_bl_2 %>% 
  select(pain_severity) %>% 
  group_by(pain_severity) %>% 
  mutate(row = sum(n())) %>% 
  distinct(.keep_all = FALSE) %>% 
  arrange(desc(row))
```

#Checking x axis range vs filtering
```{r}
mapp_bl_2 %>% 
  select(pain_severity, cohorttype) %>% 
  filter(cohorttype == 1) %>% 
  ggplot() +
  geom_histogram(aes(pain_severity), binwidth = 1, fill = "light blue", color = "black") +
  scale_x_continuous(limits = c(0, 25), breaks = seq(-1, 26, by = 2)) +
  theme_bw()
```

#Multiple Filters
```{r}
b <- 15
c <- 10

b <- as.integer(b)
c <- as.integer(c)

class(b)
class(c)

cohort_types <- c("1 - UCPPS")

data <- mapp_bl_2 %>% 
  select(urinary_severity, cohorttype2) %>% 
  filter(cohorttype2 %in% cohort_types & urinary_severity >= c & urinary_severity <= b)

nrow(data)

mapp_bl_2 %>% 
  filter(cohorttype2 %in% cohort_types) %>% 
  mutate(pain_severity = as.factor(ifelse(pain_severity < 5, "0", "1"))) %>% 
  select(pain_severity)
```

#geom_mosaic
```{r}
mapp_bl_labels %>% 
  select(agegrp, sex) %>% 
  ggplot() +
  geom_mosaic(aes(x = product(agegrp, sex), fill = sex))

mapp_bl_labels %>% 
  select(agegrp, sex) %>% 
  ggplot() +
  geom_mosaic(aes(x = product(agegrp), fill = sex)) +
  coord_flip()

mapp_bl_labels %>% 
  select(cohorttype, auasi_q1) %>% 
  ggplot() +
  geom_mosaic(aes(x = product(auasi_q1), fill = cohorttype)) +
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"), plot.subtitle = element_text(hjust = 0.5, face = "italic", size = 16), legend.position = "bottom", 
      legend.text = element_text(size = 16), legend.title = element_text(size = 16), axis.text = element_text(size = 12), 
      axis.text.x = element_text(hjust = 0.5, vjust = 0.25)) +
  coord_flip()
```

#geom_bar reference line example
```{r}
mapp_bl_2 %>% 
  select(pain_severity) %>% 
  mutate(pain_severity = as.factor(ifelse(pain_severity > 10, 1, 0))) %>% 
  drop_na() %>% 
  ggplot(aes(pain_severity, fill = pain_severity)) +
   geom_bar()

x <- 2
y <- 5

new_x <- "pain_severity"
new_y <- "urinary_severity"

jjx <- mapp_bl_2 %>%
  filter(cohorttype2 == "1 - UCPPS") %>% 
  select(new_x)

jjy <- mapp_bl_2 %>% 
  filter(cohorttype2 == "1 - UCPPS") %>% 
  select(new_y)

jjj <- mapp_bl_2 %>% 
  filter(cohorttype2 == "1 - UCPPS") %>% 
  mutate(final_x = as.factor(ifelse(jjx < x, 0, 1)), final_y = as.factor(ifelse(jjy < y, 0, 1))) %>% 
  select(final_x, final_y) %>% 
  rename({{new_x}} := final_x, {{new_y}} := final_y)

jjj %>%
 tbl_summary(
   by = new_x,
   missing = "ifany",
   type = all_categorical() ~ "categorical",
    statistic = all_categorical() ~ "{n} ({p}%)",
    digits = all_categorical() ~ c(0,1),
    missing_text = "N missing") %>%
 modify_spanning_header(all_stat_cols() ~ new_x) %>%
 modify_header(label ~ "**Variable**") %>%
 modify_caption(paste("Summary Statistics ~ ", new_x, "and ", new_y)) %>%
 as_gt()
```

#Trying regression line
```{r}
aa <- "pain_severity"
bb <- "urinary_severity"

xx <- mapp_bl_2 %>% 
  select(aa)
xx <- as.vector(xx[,1])

yy <- mapp_bl_2 %>% 
  select(bb)
yy <- as.vector(yy[,1])

model1 <- summary(lm(xx ~ yy))
model_coef <- summary(lm(urinary_severity ~ pain_severity, mapp_bl_2))$coefficients
cor_value <- round(sqrt(model1$r.squared), 2)
slope <- round(model_coef[2,1], 2)
intercept <- round(model_coef[1,1], 2)

annotation <- data.frame(
   x = c(min(mapp_bl_2$pain_severity, na.rm = TRUE) - 1, min(mapp_bl_2$pain_severity, na.rm = TRUE) - 1, min(mapp_bl_2$pain_severity, na.rm = TRUE) - 1),
   y = c(max(mapp_bl_2$urinary_severity, na.rm = TRUE) + 1, max(mapp_bl_2$urinary_severity, na.rm = TRUE) + 1, max(mapp_bl_2$urinary_severity, na.rm = TRUE) + 1),
   label = c(paste0("r = ", cor_value), paste0("slope = ", slope), paste0("intercept = ", intercept)))

ggplot(mapp_bl_2, aes(pain_severity, urinary_severity)) +
  geom_count() +
  geom_label_repel(data = annotation, aes(x = x, y = y, label = label), color = "black", size = 2.25, angle = 0, fontface = "bold", segment.color = 'transparent') +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  geom_smooth(se = FALSE) +
  theme_bw()

mapp_bl_2x <- mapp_bl_2 %>% 
  filter(cohorttype == 1 & sex == "Female")

modelx <- lm(urinary_severity ~ pain_severity, data = mapp_bl_2x)
summary(modelx)

cor.test(mapp_bl_2x$hadsanxtot, mapp_bl_2x$pain_severity)
```
#summary_e missing data and filtering observations
```{r}
x <- "urinary_severity"
y <- "auasi_q2"

filtered_data_ex <- mapp_bl_combined %>% 
  filter(cohorttype2 == "1 - UCPPS") %>% 
  dplyr::select(x, y)

filtered_data_ex %>%
      tbl_summary(
        by = y,
        missing = "always",
        type = all_continuous() ~ "continuous2",
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{N_miss}",
                                         "{median} ({p25}, {p75})",
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0,0,0,0,0,0,0,1,1)) %>%
      modify_spanning_header(all_stat_cols() ~ y) %>% 
      modify_caption("Subgroup Summary Table") %>%
      as_gt()

boop <- 0:30
sexy <- c("Male", "Female")
ucpps <- "1 - UCPPS"

filtered_data_ex2 <- mapp_bl_combined[mapp_bl_combined["urinary_severity"] >= min(boop) & mapp_bl_combined["urinary_severity"] <= max(boop) &
                  (mapp_bl_combined$cohorttype2 %in% ucpps) &
                  (mapp_bl_combined$sex %in% sexy),] %>% 
  dplyr::select(x, y)

# pp <- mapp_bl_combined %>% 
#   filter(cohorttype2 %in% ucpps & sex %in% sexy) %>% 
#   dplyr::select(x, y)
# 
# ppx <- pp %>% 
#   dplyr::select(x)
# 
# pp2 <- filter(ppx >= min(boop) & ppx <= max(boop))
#   
# 
# pp2 %>%
#       tbl_summary(
#         by = y,
#         missing = "ifany",
#         type = all_continuous() ~ "continuous2",
#         statistic = all_continuous() ~ c("{N_nonmiss}",
#                                          "{N_miss}",
#                                          "{median} ({p25}, {p75})",
#                                          "{min}, {max}",
#                                          "{mean} ({sd})"),
#         digits = all_continuous() ~ c(0,0,0,0,0,0,0,1,1)) %>%
#       modify_spanning_header(all_stat_cols() ~ y) %>% 
#       modify_caption("Subgroup Summary Table") %>%
#       as_gt()
# 
# filtered_data_ex
# filtered_data_ex2
```

#Different regression lines to account for continuous slider inputs and filtering by a 3rd variable
```{r}
reg_ex_m <- mapp_bl_2 %>% 
  select(urinary_severity, pain_severity, sex, cohorttype) %>% 
  filter(sex == "Male" & cohorttype == 1)

reg_ex_f <- mapp_bl_2 %>% 
  select(urinary_severity, pain_severity, sex, cohorttype) %>% 
  filter(sex == "Female" & cohorttype == 1)

reg_ex <- mapp_bl_2 %>% 
  select(urinary_severity, pain_severity, cohorttype) %>% 
  filter(cohorttype == 1)

reg_ex <- reg_ex %>% 
  filter(pain_severity <= 15 & urinary_severity <= 10)

summary(lm(pain_severity ~ urinary_severity, data = reg_ex))
```
#Working to achieve subgroup filtering by updating radio buttons through variable manipulation
```{r}
bb <- mapp_bl_combined %>%
    gather(columnNames, values) %>% 
    group_by(columnNames) %>% 
    distinct(.keep_all = TRUE) %>% 
    drop_na()

x <- "agegrp"
xy <- "1 - UCPPS"
yy <- "1: <35 years"
      
mapp_bl_combined %>%
  filter(cohorttype2 %in% xy & x %in% yy)

gg <- mapp_bl_combined %>% 
  pull(x)

mapp_bl_combined %>% 
  select(urinary_severity, pain_severity)

mapp_bl_combined %>%
      select(cohorttype) %>% 
      gather(columnNames, values) %>% 
      distinct(.keep_all = TRUE) %>% 
      pull(values)
```

**MAPP II Baseline**

#Dictionary
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_dict_II <- read.csv("variable_dict_II.csv") %>% 
  select(1:11)
```

#Variable Assignments 3, 4, 5
```{r}
variable_assignments_3_II <- mapp_dict_II %>% 
  slice(1:910) %>% 
  mutate(variable = as.character(NAME), variable_selection = as.character(Primary_Grouping), label = as.character(LABEL)) %>% 
  mutate(ANALYSIS_TYPE_2 = ifelse(ANALYSIS_TYPE == 1, "1 - Continuous", ifelse(ANALYSIS_TYPE == 2, "2 - Ordinal", ifelse(ANALYSIS_TYPE == 3, "3 - Nominal", "4 - Binary")))) %>% 
  select(variable, variable_selection, ANALYSIS_TYPE, ANALYSIS_TYPE_2, label) %>% 
  filter(variable != "pid" & variable != "zip_first3")
```

#MAPP BL 2 II
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_bl_2_II <- read.csv("mapp_bl_2_II.csv") %>%
  mutate(cohorttype2 = ifelse(cohorttype == 1, "1 - UCPPS", ifelse(cohorttype == 2, "2 - Healthy Controls", "3 - Positive Controls")), sex = ifelse(sex == 1, "Male", "Female")) %>% 
  select(-pid)

mapp_bl_cohort_II <- mapp_bl_2_II %>% 
  select(cohorttype2) %>% 
  distinct(cohorttype2, .keep_all = TRUE)

mapp_bl_sex_II <- mapp_bl_2_II %>% 
  select(sex) %>% 
  distinct(sex, .keep_all = TRUE)

mapp_bl_primary_II <- variable_assignments_3_II %>% 
  select(variable_selection) %>% 
  distinct() %>% 
  arrange(variable_selection)
```

#MAPP Labels
```{r}
setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
mapp_bl_labels_II <- read.csv("mapp_bl_label_II.csv") %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Healthy Controls", "2 - Healthy Controls", "3 - Positive Controls")),
         sex = ifelse(sex == "1: Male", "Male", "Female"), bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat)) %>%
  select(-pid)
mapp_bl_labels_II[mapp_bl_labels_II == ""] <- NA

variable_assignments_4_II <- variable_assignments_3_II %>% 
  filter(ANALYSIS_TYPE != 1 & variable != "pid")

variable_assignments_5_II <- variable_assignments_3_II %>% 
  filter(ANALYSIS_TYPE == 1 & variable != "pid")

factored_II <- mapp_bl_labels_II %>%
  select(any_of(variable_assignments_4_II$variable)) %>%
  mutate_if(is.numeric, as.factor)

continuous_II <- mapp_bl_2_II %>%
  select(any_of(variable_assignments_5_II$variable))

mapp_bl_combined_II <- data.frame(factored_II, continuous_II) %>%
  mutate(cohorttype2 = ifelse(cohorttype == "1: UCPPS", "1 - UCPPS", ifelse(cohorttype == "2: Controls", "2 - Healthy Controls", "3 - Positive Controls")),
         bpi_region_notpp_cat = ifelse(bpi_region_notpp_cat == "0:00", "0: 0", bpi_region_notpp_cat))

setwd("/Users/flynnmc/Desktop/UPenn/Flynn MAPP Items")
full_labels_II <- read_csv("full_labels_II.csv") %>% 
  drop_na()
```

#Plots with missing values
```{r}
mapp_bl_2_example <- mapp_bl_combined %>%
  filter(cohorttype == "1: UCPPS") %>% 
  select(urinary_severity, auasi_q3) %>% 
  drop_na(urinary_severity) %>% 
  mutate_if(is.factor, fct_explicit_na, na_level = "Missing Observation")

mapp_bl_2_example_2 <- mapp_bl_combined %>%
  filter(cohorttype == "1: UCPPS") %>% 
  select(urinary_severity, auasi_q3) %>% 
  drop_na()

ggplot(mapp_bl_2_example, aes(urinary_severity, color = auasi_q2, fill = auasi_q2)) + 
      geom_histogram(binwidth = 1, position = "stack", alpha = 0.5) +
      scale_x_continuous(limits = c(-1, 26), breaks = seq(0, 25, by = 2)) +
      theme_bw() +
      labs(x = "", y = "Count", fill = str_wrap(y, 25), color = str_wrap(y, 25), title = str_wrap(x, 70), 
           subtitle = paste("Number of Observations: ", nrow(mapp_bl_2_example))) +
      theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"), plot.subtitle = element_text(hjust = 0.5, face = "italic", size = 16), 
            axis.title = element_text(size = 16, face = "bold"), legend.position = "bottom", axis.text = element_text(size = 18), legend.text = element_text(size = 16), 
            legend.title = element_text(size = 16), plot.caption = element_text(hjust = 0, size = 14, face = "bold"))

ggplot(mapp_bl_2_example_2, aes(urinary_severity, color = auasi_q2, fill = auasi_q2)) + 
      geom_histogram(binwidth = 1, position = "stack", alpha = 0.5) +
      scale_x_continuous(limits = c(-1, 26), breaks = seq(0, 25, by = 2)) +
      theme_bw() +
      labs(x = "", y = "Count", fill = str_wrap(y, 25), color = str_wrap(y, 25), title = str_wrap(x, 70), 
           subtitle = paste("Number of Observations: ", nrow(mapp_bl_2_example_2))) +
      theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"), plot.subtitle = element_text(hjust = 0.5, face = "italic", size = 16), 
            axis.title = element_text(size = 16, face = "bold"), legend.position = "bottom", axis.text = element_text(size = 18), legend.text = element_text(size = 16), 
            legend.title = element_text(size = 16), plot.caption = element_text(hjust = 0, size = 14, face = "bold"))
```

#Testing summaries
```{r}
mapp_bl_2_example %>%
      tbl_summary(
        by = auasi_q3,
        missing = "ifany",
        missing_text = "Missing Observations",
        type = all_continuous() ~ "continuous2",
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})",
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0,0,0,0,0,0,0,1,1)) %>%
      modify_spanning_header(all_stat_cols() ~ paste("auasi_q2")) %>% 
      modify_header(label ~ paste("urinary_severity")) %>% 
      modify_caption("Subgroup Summary Table") %>%
      as_gt()

mapp_bl_2_example_2 %>%
      tbl_summary(
        by = auasi_q3,
        missing = "ifany",
        missing_text = "Missing Observations",
        type = all_continuous() ~ "continuous2",
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})",
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0,0,0,0,0,0,0,1,1)) %>%
      modify_spanning_header(all_stat_cols() ~ paste("auasi_q2")) %>% 
      modify_header(label ~ paste("urinary_severity")) %>% 
      modify_caption("Subgroup Summary Table") %>%
      as_gt()
```

#Merging tables
```{r}
mapp_ex <- mapp_bl_combined %>%
  filter(cohorttype == "1: UCPPS")

q1 <- mapp_ex %>% 
        select(urinary_severity) %>% 
        tbl_summary(
          missing = "ifany",
          missing_text = "Missing Observations",
          type = all_continuous() ~ "continuous2",
          statistic = all_continuous() ~ c("{N_nonmiss}",
                                           "{median} ({p25}, {p75})", 
                                           "{min}, {max}",
                                           "{mean} ({sd})"),
          digits = all_continuous() ~ c(0,0,0,0,0,0,1,1)) %>% 
        modify_spanning_header(all_stat_cols() ~ "**Summary Statistics**") %>% 
        modify_header(label ~ "**Variable**") %>%
        modify_caption(paste("Summary Statistics"))
      
q2 <- mapp_ex %>% 
  select(pain_severity) %>% 
  tbl_summary(
          missing = "ifany",
          missing_text = "Missing Observations",
          type = all_continuous() ~ "continuous2",
          statistic = all_continuous() ~ c("{N_nonmiss}",
                                           "{median} ({p25}, {p75})", 
                                           "{min}, {max}",
                                           "{mean} ({sd})"),
          digits = all_continuous() ~ c(0,0,0,0,0,0,1,1)) %>% 
        modify_spanning_header(all_stat_cols() ~ "**Summary Statistics**") %>% 
        modify_header(label ~ "**Variable**") %>%
        modify_caption("Summary Statistics")
      
tbl_merge(tbls = list(q1, q2)) %>%
  modify_spanning_header(everything() ~ NA_character_) %>% 
  modify_footnote(all_stat_cols() ~ paste("cohort_label_2()", " | ", "filter_label_2()", "|", "dataset_subtitle_II()")) %>% 
  as_gt()
```

#Creating dataframe for the for loop
```{r}
cohort_type <- "1 - UCPPS"
subgroup_options <- c("2: Less than half the time", "4: More than half the time")

hi <- mapp_bl_combined[(mapp_bl_combined$cohorttype2 %in% cohort_type),] %>% 
     select(pain_severity, auasi_q1)

`%notin%` <- Negate(`%in%`)

jj <- factored %>% 
  select(auasi_q1) %>% 
  distinct() %>% 
  gather(columnNames, values) %>% 
  mutate(stat_count = substr(values, 1, 1)) %>% 
  select(stat_count) %>% 
  drop_na()

oo <- if(0 %notin% jj$stat_count) {
  factored %>% 
  select(auasi_q1) %>% 
  distinct() %>% 
  gather(columnNames, values) %>% 
  mutate(stat_count = substr(values, 1, 1)) %>% 
  filter(values %notin% subgroup_options) %>% 
  select(stat_count) %>% 
  drop_na()

} else {
  factored %>% 
  select(auasi_q1) %>% 
  distinct() %>% 
  gather(columnNames, values) %>% 
  mutate(stat_count = substr(values, 1, 1)) %>% 
  filter(values %notin% subgroup_options) %>% 
  select(stat_count) %>% 
  drop_na() %>% 
  mutate(stat_count = as.integer(stat_count) + 1)
}
```

#Testing if for loop for summary works
```{r}
ww <- NULL
for (i in nrow(oo)) {
  ww <- paste0("stat_", oo$stat_count)
}

if(ww == "stat_") {
  hi %>% 
      tbl_summary(
        by = auasi_q1,
        missing = "ifany",
        missing_text = "Missing Observations",
        type = all_continuous() ~ "continuous2",
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})", 
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0,2,2,2,0,0,2,2)) %>% 
      modify_spanning_header(all_stat_cols() ~ "**Summary Statistics**") %>%
      modify_header(label ~ "paste(x)") %>%
      modify_caption("Summary Table") %>%
      modify_footnote(all_stat_cols() ~ "Hi") %>%
      as_gt()
  
} else {
  hi %>% 
      tbl_summary(
        by = auasi_q1,
        missing = "ifany",
        missing_text = "Missing Observations",
        type = all_continuous() ~ "continuous2",
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})", 
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0,2,2,2,0,0,2,2)) %>% 
      modify_spanning_header(all_stat_cols() ~ "**Summary Statistics**") %>%
      modify_header(label ~ "paste(x)") %>%
      modify_caption("Summary Table") %>%
      modify_footnote(all_stat_cols() ~ "Hi") %>%
      modify_column_hide(columns = all_of(ww)) %>% 
      as_gt()
}
```

#Fixing healthy controls summary bug
```{r}
mapp_bl_combined %>% 
  select(gupiscoreqol, cohorttype2, race_aa) %>% 
  filter(cohorttype2 == "2 - Healthy Controls") %>% 
  drop_na(gupiscoreqol, race_aa) %>% 
      tbl_summary(
        by = race_aa,
        missing = "ifany",
        missing_text = "Missing Observations",
        type = list(where(is.numeric) ~ "continuous2"),
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})",
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0, 2, 2, 2, 0, 0, 2, 2)) %>%
      modify_spanning_header(all_stat_cols() ~ "paste(y)") %>% 
      modify_header(label ~ "paste(x)") %>% 
      modify_caption("Subgroup Summary Table") %>%
      modify_footnote(all_stat_cols() ~ "Hi") %>% 
      add_p(pvalue_fun = ~style_pvalue(.x, digits = 3))

pp <- mapp_bl_combined %>% 
  select(gupiscoreqol, cohorttype2, race_aa) %>% 
  filter(cohorttype2 == "2 - Healthy Controls") %>% 
  select(gupiscoreqol) %>% 
  mutate(gupiscoreqol = as.numeric(gupiscoreqol))
```

#Testing Regression
```{r}
reg_a <- lm(pain_severity ~ urinary_severity, mapp_bl_combined)
    
    reg_a %>% 
      tbl_regression(
        pvalue_fun = ~style_pvalue(.x, digits = 3),
        intercept = TRUE
      ) %>% 
      bold_labels() %>% 
      modify_footnote(all_stat_cols() ~ paste("Response Variable ~", "pain_severity")) %>% 
      as_gt()
    
pp <- mapp_bl_combined %>% 
  pull(pain_severity)

qq <- mapp_bl_combined %>% 
  pull(urinary_severity)

lm(pp ~ qq, mapp_bl_combined)
```

#Longitudinal Graphs
```{r}
mapp_long_combined %>% 
  ggplot(aes(vnum, pain_severity, group = pid)) +
  geom_line() +
  facet_wrap(. ~ sex)

mapp_long_combined %>% 
 ggplot(aes(vnum, pain_severity, group = pid, color = sex)) + 
  geom_line() +
  facet_wrap(. ~ auasi_q1) +
  theme(legend.position = "none")
```

#Testing Longitudinal Datasets
```{r}
mapp_long_combined %>%
      gather(columnNames, values) %>% 
      group_by(columnNames) %>% 
      distinct(.keep_all = TRUE) %>% 
      drop_na()
```

#More long plots
```{r}
mapp_long_combined %>% 
  select(vnum, pain_severity, rice_bps_bin) %>% 
  drop_na(rice_bps_bin) %>% 
  ggplot(aes(as.factor(vnum), pain_severity, color = rice_bps_bin)) +
  geom_violin(trim = FALSE, na.rm = TRUE) +
  stat_summary(fun.data = "mean_sdl", fun.args = list(mult = 1), geom = "pointrange", color = "black") +
  theme_bw() +
  facet_wrap(. ~ rice_bps_bin) +
  theme(legend.position = "none")

mapp_long_combined %>% 
  ggplot(aes(vnum, age, group = pid)) +
  geom_line(color = "gray", alpha = 0.7) + 
  stat_smooth(aes(group = 1), se = FALSE) +
  stat_summary(aes(group = 1), geom = "point", fun = mean, shape = 16, size = 2, color = "black")

mapp_long_combined %>% 
  ggplot(aes(vnum, auasi_total, group = pid)) +
  geom_line() +
  geom_line(color = "gray", alpha = 0.7) + 
  stat_smooth(aes(group = 1), se = FALSE, method = lowess) +
  stat_summary(aes(group = 1), geom = "point", fun = mean, shape = 16, size = 2, color = "black") +
  stat_summary(aes(group = 1), geom = "point", fun = median, shape = 8, size = 2, color = "black") +
  theme_bw()

mapp_long_combined %>% 
  ggplot(aes(vnum, pain_severity, group = pid)) +
  geom_line(color = "gray", alpha = 0.4) + 
  facet_wrap(. ~ rice_subtype_3lev) +
  stat_smooth(aes(group = 1), se = FALSE) +
  stat_summary(aes(group = 1), geom = "point", fun = median, shape = 8, size = 1, color = "black") +
  stat_summary(aes(group = 1), geom = "line", fun = median, color = "black", size = 0.2) +
  theme_bw()
```

#Longitudinal Tables
```{r}
mapp_long_combined %>% 
  filter(vnum <= 5) %>% 
  mutate(vnum = as.factor(vnum)) %>% 
  select(pain_severity, vnum) %>% 
  tbl_summary(
    by = vnum,
    missing = "ifany",
    missing_text = "Missing Observations",
    type = list(where(is.numeric) ~ "continuous2"),
    statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})", 
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
    digits = all_continuous() ~ c(0, 2, 2, 2, 0, 0, 2, 2)
  )
```

#Multiple GGPlot Choices
```{r}
library(ggplot2)
library(tidyverse)

ss = TRUE
if(ss == TRUE) {
  ggplot2::ggplot(data = iris)
} else {
  ggplot2::ggplot(data = iris) + aes(Sepal.Length, Sepal.Width)
}

p = ggplot2::ggplot(data = iris)

fun1 = function(x, ss) {
  if(ss == TRUE) {
    x
  } else {
    x + aes(Sepal.Length, Sepal.Width)
  }
}

p %>% 
  fun1(., ss = FALSE) + 
  geom_line()
```

#Playing with continuous variables
```{r}
variable_assignments_long_5 %>% 
  distinct(variable_selection) %>% 
  arrange(variable_selection)
  
mapp_long_combined %>% 
  filter(agegrp)
  select(age, vnum) %>% 
  drop_na()

test <- "Demographics/Anthropometrics"
sort(variable_assignments_long_5[variable_assignments_long_5$variable_selection %in% test, "variable", drop = TRUE])

w <- mapp_long %>% 
      pull(vnum)
    
    max_v <- round(round(max(w, na.rm = TRUE)))
    min_v <- floor(floor(min(w, na.rm = TRUE)))
    
mapp_long_combined %>% 
  filter(sex == c(5, 4)) %>% 
  select(vnum)
```

#gt_summary slider into categorical variable issue
```{r}
filtered_data_2a() %>% 
      select(input$variable_choice) %>% 
      tbl_summary(
        missing = "ifany",
        missing_text = "Missing Observations",
        type = all_continuous() ~ "continuous2",
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})", 
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0, 2, 2, 2, 0, 0, 2, 2))

mapp_bl_combined %>% 
  select(pain_severity, cohorttype) %>% 
  filter(pain_severity < 8, cohorttype == "1: UCPPS") %>% 
  select(pain_severity) %>% 
  tbl_summary(
    missing = "ifany",
        missing_text = "Missing Observations",
        type = list(where(is.numeric) ~ "continuous2"),
        statistic = all_continuous() ~ c("{N_nonmiss}",
                                         "{median} ({p25}, {p75})", 
                                         "{min}, {max}",
                                         "{mean} ({sd})"),
        digits = all_continuous() ~ c(0, 2, 2, 2, 0, 0, 2, 2))
```


